
# The following code provide information to recreate a map with sample locations and any other kind of variables on a Google Map.

## Set Working directory

```{r}
setwd("C:/PathToTheFiles")
```

## Install the required packages 

```{r}
install.packages("ggmap")
install.packages("ggrepel")
```

## Create a pop coordinates object

### The Boar_info.txt file was NOT providing any geographic locations but only town or park names. We got the spatial coordinates from these locations with google map.

```{r}
pop_coor <- read.table("Boar_info_coor.txt", sep="\t", h=T, stringsAsFactors = F)
View(pop_coor)
```

### The following code allows to plot the sample locations on a Google Map. First let's set the parameters for the map: loc is the geolocation where the map will be centered (here it is the average of the latitudes and longitudes with latitute - 0.5 because of few samples far south), zoom is the value of zoom and maptype one of the four map options provided by Google.

```{r}
library(ggmap)

loc <- apply(pop_coor[, 10:9], 2, mean)
loc[2]  <- loc[2] - 0.5
zoom <- 7
#maptype <-"satellite" # Here select the one according what map you want
#maptype <-"terrain"
maptype <-"hybrid"
#maptype <-"roadmap"
```

### Then we download the map and plot it with the element from the data table we want (here the samples locations and the cluster column).

```{r}
map <- get_map(location = loc, zoom = zoom, maptype = maptype)
ggmap(map) + geom_point(data = pop_coor, aes(long, lat, colour = factor(clusters)), size=5)
```

### Next we plot the names of the hybrids only and let's add some labels.

```{r}
library(ggrepel)
ggmap(map) + geom_point(data = pop_coor, aes(long, lat, colour = factor(clusters)), size=5) +
                  labs(x = 'Longitude', y = 'Latitude') +
                  geom_label_repel(data = subset(pop_coor, PCA.cluster %in% c("hyb1", "hyb2", "hyb3", "hyb4", "hyb5", "hyb6", "hyb7", "hyb8", "hyb9")), aes(x = long, y = lat, label = PCA.cluster), 
                  fill = "white", box.padding = unit(.4, "lines"),
                  label.padding = unit(.15, "lines"),
                  segment.color = "grey", segment.size = 1)
```
